\cvparagraph{About Me}
I am planning to graduate in 2020 with a B.S./M.S. and master's thesis in the \MYhref{https://www.colorado.edu/aerospace/current-students/graduates/curriculum/autonomous-systems}{autonomous systems} focus within CU Boulder's Aerospace Engineering program. During my undergraduate studies in the aerospace engineering department, I focused both of my undergraduate minors - Computer Science and Applied Math - on building the educational foundation needed to be a competent software engineer with a strong background in dynamical systems. During my most recent R\&D internships (at \MYhref{http://lasp.colorado.edu}{LASP} and then at \MYhref{https://www.siemensgamesa.com/en-int}{Siemens Gamesa}), I consistently sought out projects and mentorships that allowed me to develop software products in support of the main engineering efforts. Using my engineering foundation, I moved on to study robotics and autonomy during my time as a M.S student. I’ve found, through my thesis research, that this field has a wealth of challenging, inspirational problems that fuel my passion for robotics and autonomy.

I thrive in a collaborative engineering environment. Last year, I was project manager for \MYhref{https://www.colorado.edu/aerospace/current-students/undergraduates/senior-design-projects/past-senior-projects/2018-2019/vantage}{my year-long senior project} where I lead 10 engineers in the development, manufacture, and V\&V of computer vision hardware (monochrome and LiDAR cameras) and software to augment Space Situational Awareness from the ISS. Our team delivered a quality product; our customer funded another year of development, we won multiple awards from our college, and our
\MYhref{https://digitalcommons.usu.edu/smallsat/2019/all2019/141/}{conference paper} won 2\textsuperscript{nd} place and \$7500 at the  \MYhref{https://smallsat.org/students/previous-winners}{2019 SmallSat FJR student competition}. My team was successful because we prioritized having diverse team members and a fun and relaxed team atmosphere where success was celebrated and failure encouraged. I am proud to say that I learned as much about my team members' cultural backgrounds and lifestyles as I did about our technical challenges.