\cvparagraph{Why Waymo?}
Ever since I made the decision to focus my career on autonomous systems, I have aspired to work at Waymo to make the future of self-driving transportation a reality. More so than other self-driving transportation ventures, I am attracted to Waymo because the company has such a deliberate focus on safety. From Waymo's actual mission statement to ``make it safe and easy for people and things to move around", to how you have amassed millions of miles of on-road testing and class-leading miles per disengagement before starting the productization process, your safety-centric methodology for maturing self-driving technology meshes extremely well with my own passion for safe autonomy, an integral facet of my thesis work. 

My \MYhref{https://www.ariasystems.group/}{research group} and my own research are both motivated by the need to think of the safety of autonomous systems not just as an aspect of system design, but rather as the driver of the whole design process. My research focuses on ways to join machine learning, control theory, and formal methods to synthesize principled, auditable, and safe learning based decision-making systems. My research group sees growing interest from industry and the government in provable safety of safety-critical systems, motivated by the need to ensure both performance and public trust in said systems. Waymo consistently demonstrates leadership in this regard.

I see a promising future at Waymo, and I am confident that, with my engineering expertise and interest in safe, performant autonomy, I will be a strong asset to the organization.